Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-17 Latex/tex/pr.tex
mat file
add fig

\begin{abstract}
Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a global 'carrier-led' effort to bring greater transparency of Open-RAN 
(O-RAN), to the next-generation of radio access network. \newline
To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method in 5G in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network. \newline
In this paper, we elaborates joint NS in RAN and Core of O-RAN system and investigate optimal power 
of each User Equipment (UE) to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel. The problem is formulated as a mixed integer optimization problem that can be decompose into two independent sub-problems for RAN and Core. 
Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously map slices to services and optimize power and the second sub-problem in order to map slices to physical resources and minimize number of active Data Centers (DC).
\end{abstract}

@@

There are two main ideas here: According to real-time analytics which is used for artificial intelligence system is evolving the radio access networks to make them more open and smarter than previous generations. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces. \newline
The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented.\newline
xRAN technology has three fundamental feature. Control plane is decoupled from User plane. In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces is introduced.

@@

    \includegraphics[scale=0.45]{c2}

@@

Responsibility of wireless systems of the fifth generation covers a wide range types of services. In order to provide the requirement of these services, Network Slicing (NS) is implemented to virtualize the common physical network into several logical end-to-end networks. \newline
To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity. Compression of message which is passed through these links, is a consequence of limited fronthaul capacity.\\
Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data. Also VNFs are mapped to physical resource through NS technique. \newline
In this paper, in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 

@@

>>>>

\begin{abstract}
Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a global 'carrier-led' effort to bring greater transparency of Open-RAN 
(O-RAN), to the next-generation of radio access network. \newline
To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method in 5G in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network. \newline
In this paper, we elaborates joint NS in RAN and Core of O-RAN system and investigate optimal power 
of each User Equipment (UE) to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel. The problem is formulated as a mixed integer optimization problem that can be decompose into two independent sub-problems for RAN and Core since sub-problems are independent. 
Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously map slices to services and optimize power and the second sub-problem in order to map slices to physical resources and minimize number of active Data Centers (DC).
\end{abstract}

@@

The Idea of O-RAN comes from two opinion. Firstly, according to real-time analytic used for artificial intelligence system, the radio access networks must be evolved to be more open and smarter than previous generations. Furthermore, O-RAN can virtualize elements of the network with  appropriate interfaces \cite{orant}. \newline
The core idea driving C-RAN is to split radio remote head (RRH) and baseband unit (BBU). Several BBUs operating on a cloud server will create a BBU-pool, providing unified baseband signal processing with powerful computing capabilities. Moreover, in O-RAN technology, this separation is implemented\cite{cran1}.
To communicate between BBU-pool and RRHs, fronthaul interface which is fiber link is assumed with limited capacity. Compression of message which is passed through these links, is a consequence of limited fronthaul capacity\cite{frdl,simeone2016cloud}.
Each VM has a computing processor which is mapped to Virtual Network Functions (VNFs) which is processed arrival data. Also VNFs are mapped to physical resource through NS technique\cite{frdl,luong2018novel,luong2018novel1}. 
xRAN technology ,released in April 2018 as a next generation of RAN, has three fundamental features. Control plane is decoupled from User plane. In addition, a modular eNB software stack is built to operate on common-off-the-shelf (COTS) hardware. Moreover, open north-bound and south-bound interfaces is introduced\cite{xran}.

@@

    \includegraphics[scale=0.55]{c2}

@@

Responsibility of wireless systems of the fifth generation covers a wide range types of services. In order to provide the requirement of these services, NS is implemented to virtualize the common physical network into several logical end-to-end networks. Three different types of NS is introduced in \cite{ns1} contains Core Slicing, RAN Slicing and Core-RAN Slicing. In Core-RAN Slicing, each slice of RAN is mapped to slices of Core.    
In this paper, as  mentioned in figure \eqref{fig:c11}, the downlink of O-RAN system is assumed. UEs are divided to different groups according to 

@@

    \includegraphics[scale=0.5]{fig1}
  \caption{algorithm}
